---
title: "Introduction to Regression in R"
author: "Elvin"
date: "2024-05-27"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Load data

```{r loading data, warning=FALSE}

library(dplyr)
library(tidyr)
library(ggplot2)
library(readr)
library(broom)
library(ggfortify)
library(fst)

Taiwan_real_estate <- read_fst("/home/ea358/Introduction_to_Regression/taiwan_real_estate.fst")
ad_conversion <- read_fst("/home/ea358/Introduction_to_Regression/ad_conversion.fst")
churn_data <- read_fst("/home/ea358/Introduction_to_Regression/churn.fst")

View(Taiwan_real_estate)
View(ad_conversion)
View(churn_data)
```

## 2. Visualizing two variables

```{r loading data, warning=FALSE}

ggplot(Taiwan_real_estate, aes(x = n_convenience, y = price_twd_msq)) +
  geom_point(alpha = 0.5) + 
  geom_smooth(method = "lm", se = FALSE)
```
## 3. Visualizing two variables

```{r loading data, warning=FALSE}

lm(price_twd_msq ~ n_convenience, Taiwan_real_estate)
```
## 4. Visualizing numeric vs. categorical

```{r loading data, warning=FALSE}

ggplot(Taiwan_real_estate, aes(price_twd_msq)) +
  geom_histogram(bins=10) +
  facet_wrap(vars(house_age_years))
```

## 5. Calculating means by category

```{r loading data, warning=FALSE}

summary_stats <- Taiwan_real_estate %>% 
  group_by(house_age_years) %>% 
  summarise(mean_by_group = mean(price_twd_msq))

summary_stats
```
## 6. lm() with a categorical explanatory variable

```{r loading data, warning=FALSE}

mdl_price_vs_age <- lm(price_twd_msq ~ house_age_years, Taiwan_real_estate)
mdl_price_vs_age1 <- lm(price_twd_msq ~ house_age_years + 0, Taiwan_real_estate)

mdl_price_vs_age
mdl_price_vs_age1
```

## 7. Predicting house prices

```{r loading data, warning=FALSE}

explanatory_data <- tibble(n_convenience = 0:10)

mdl_price_vs_conv <- lm(price_twd_msq ~ n_convenience, Taiwan_real_estate)

prediction_data <- explanatory_data %>% 
  mutate(price_twd_msq = predict(mdl_price_vs_conv, explanatory_data))

prediction_data
```

## 8. Visualizing predictions

```{r loading data, warning=FALSE}

ggplot(Taiwan_real_estate, aes(n_convenience, price_twd_msq)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  geom_point(data = prediction_data, aes(x = n_convenience, y = price_twd_msq), color = "yellow")
```

## 9. Extracting model elements

```{r loading data, warning=FALSE}

coefficients(mdl_price_vs_conv)
fitted(mdl_price_vs_conv)
residuals(mdl_price_vs_conv)
summary(mdl_price_vs_conv)
```

## 10. Using broom

```{r loading data, warning=FALSE}

tidy(mdl_price_vs_conv)
augment(mdl_price_vs_conv)
glance(mdl_price_vs_conv)
```

## 11. Transforming the explanatory variable

```{r loading data, warning=FALSE}

plot1 <- ggplot(Taiwan_real_estate, aes(sqrt(dist_to_mrt_m), price_twd_msq)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

plot1

mdl_price_vs_dist <- lm(price_twd_msq ~ sqrt(dist_to_mrt_m), Taiwan_real_estate)
mdl_price_vs_dist

explanatory_data <- tibble(dist_to_mrt_m = seq(0, 80, 10) ^ 2)

prediction_data <- explanatory_data %>% 
  
mutate(price_twd_msq = predict(mdl_price_vs_dist, explanatory_data))

prediction_data

plot2 <- ggplot(Taiwan_real_estate, aes(sqrt(dist_to_mrt_m), price_twd_msq)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  geom_point(data = prediction_data, color = "green", size = 5)

plot2
```

## 12. Transforming the response variable

```{r loading data, warning=FALSE}

plot3 <- ggplot(ad_conversion, aes(n_impressions ^ 0.25, n_clicks ^ 0.25)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

plot3

mdl_click_vs_impression_orig <- lm(n_clicks  ~ n_impressions, data = ad_conversion)
mdl_click_vs_impression_trans <- lm(I(n_clicks ^ 0.25) ~ I(n_impressions ^ 0.25), data = ad_conversion)

explanatory_data <- tibble(n_impressions = seq(0, 3e6, 5e5))

prediction_data1 <- explanatory_data %>% 
  mutate(n_clicks_025 = predict(mdl_click_vs_impression_trans, explanatory_data),
        n_clicks = n_clicks_025 ^ 4) 

prediction_data1

ggplot(ad_conversion, aes(n_impressions ^ 0.25, n_clicks ^ 0.25)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  geom_point(data = prediction_data1, aes(x = n_impressions ^ 0.25, y = n_clicks_025), color = "green", size = 5)
```

## 13. Coefficient of determination

```{r loading data, warning=FALSE}

summary(mdl_click_vs_impression_orig) 
summary(mdl_click_vs_impression_trans)


glance(mdl_click_vs_impression_orig) %>% 
pull(r.squared)


glance(mdl_click_vs_impression_trans) %>% 
pull(r.squared)
```

## 14. Residual standard error

```{r loading data, warning=FALSE}

glance(mdl_click_vs_impression_orig) %>% 
pull(sigma)


glance(mdl_click_vs_impression_trans) %>% 
pull(sigma)
```

## 15. Drawing diagnostic plots

```{r loading data, warning=FALSE}

autoplot(mdl_price_vs_conv, which = 1:3, nrow = 3, ncol = 1)

```

## 16. Extracting leverage and influence

```{r loading data, warning=FALSE}

mdl_price_vs_dist %>% 
  augment %>% 
  arrange(desc(.hat)) %>% 
  head()


autoplot(mdl_price_vs_dist, which = 4:6, nrow = 3, ncol = 1)
```

## 17. Exploring the explanatory variables - Churn data

```{r loading data, warning=FALSE}

ggplot(churn_data, aes(time_since_last_purchase)) +
  geom_histogram(binwidth = 0.25) +
  facet_grid(rows = vars(has_churned))



ggplot(churn_data, aes(time_since_first_purchase)) +
  geom_histogram(binwidth = 0.25) +
  facet_grid(rows = vars(has_churned))
```

## 18. Visualizing linear and logistic models

```{r loading data, warning=FALSE}

  ggplot(churn_data, aes(time_since_first_purchase, has_churned)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red") + 
  geom_smooth(method = "glm", se = FALSE, method.args = list(family = binomial))

  plt_churn_vs_relationship <- ggplot(churn_data, aes(time_since_first_purchase, has_churned)) +
  geom_point() + 
  geom_smooth(method = "glm", se = FALSE, method.args = list(family = binomial))

  plt_churn_vs_relationship
```

## 19. Logistic regression with glm()

```{r loading data, warning=FALSE}

mdl_churn_vs_relationship <- glm(has_churned ~ time_since_first_purchase, data = churn_data, family = binomial)
mdl_churn_vs_relationship
```

## 20. Probabilities

```{r loading data, warning=FALSE}

explanatory_data <- tibble(time_since_first_purchase = seq(-1.5, 4, 0.25))

prediction_data <- explanatory_data %>% 
  mutate(has_churned = predict(mdl_churn_vs_relationship, explanatory_data, type = "response"),
  most_likely_outcome = round(has_churned))

plt_churn_vs_relationship +
  geom_point(aes(y = most_likely_outcome),
    data = prediction_data, 
    color = "yellow", 
    size = 2)
```

## 21. Odds ratio

```{r loading data, warning=FALSE}

prediction_data1 <- explanatory_data %>% 
  mutate(has_churned = predict(mdl_churn_vs_relationship, explanatory_data,type = "response"),
  odds_ratio = has_churned/(1-has_churned)) 

  ggplot(prediction_data1, aes(time_since_first_purchase, odds_ratio)) +
  geom_line() +
  geom_hline(yintercept = 1, linetype = "dotted")


prediction_data1
```

## 22. Log odds ratio

```{r loading data, warning=FALSE}

prediction_data2 <- explanatory_data %>% 
  mutate(has_churned = predict(mdl_churn_vs_relationship, explanatory_data, type = "response"),
    odds_ratio = has_churned / (1 - has_churned),
    log_odds_ratio = log(odds_ratio),
    log_odds_ratio2 = predict(mdl_churn_vs_relationship, explanatory_data))

# See the result
prediction_data2
```